Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-22 ms.tex
editing

\begin{eqnarray}
  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}
  &\approx& 12\eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
    Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} \nonumber \\
  &\approx& 12 M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}
\label{eq:rIars}
\end{eqnarray}
{\bf AG-Note the different scaling relations here.}
If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
approximated as a steady heating source near the stagnation radius for
extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
h}$).  On the other hand, equation (\ref{eq:rIars}) may underestimate
the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
if the heating rate excluding SN Ia is less than this.

>>>>

\begin{eqnarray}
  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}
  &\approx& 12\eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
    Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} \nonumber \\
  &\approx& 12 M_{\bullet,8}^{-1.1}(\epsilon_{\rm Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}
\label{eq:rIars}
\end{eqnarray}
If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
approximated as a steady heating source near the stagnation radius for
extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
h}$).  On the other hand, equation (\ref{eq:rIars}) may underestimate
the importance of Ia heating because $r_{\rm Ia}/r_{\rm s}$ will be
substantially smaller than its value estimated using $v_{w}^{\rm Ia}$
if the heating rate excluding SN Ia is less than this.
